\mytitle

### 2017-11-03 paper.tex
nits

\newcommand{\xxx}[0]{\textsc{APUS}\xspace}
\newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
\newcommand{\mytitle}[0]{\textbf {Study Report}}
\newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
and Deterministic Multithreading, Software Reliability}

@@

\begin{sloppypar}
State machine replication (\smr) is a powerful fault-tolerance 
concept~\cite{paxos:practical}. It runs replicas 
of same program on multiple nodes. To keep the replicas consistent, it invokes a 
distributed consensus protocol (typically 
\paxos~\cite{paxos:simple,lamport98parttime,paxos:complex}) to ensure that a 
quorum (typically majority) of the replicas agree on the input request sequence. 
\smr is proven to tolerate various failure scenarios, like network 
partition and packet loss.

The fault-tolerant benefit of \smr makes it particularly an attractive 
high-availability service for general server programs. Unfortunately, despite 
much effort, existing \smr systems are still hard to deploy, mainly due to 
three problems.

\textbf{High consensus latency.} The consensus latency of traditional \paxos 
protocols is notoriously high, incurring high performance overhead for server 
programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
protocols have to go through OS kernel. For efficiency, \paxos protocols 
typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
replica as the ``leader'' to invoke consensus requests, and the other replicas 
as ``backups'' to agree on requests. To agree on an input, at least one 
round-trip time (RTT) is required between the leader and a backup. Given that a 
ping RTT in LAN typically takes hundreds of \us, and that the request processing 
time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
existing \paxos protocols incur high overhead in the response time of server 
programs.

\textbf{Poor scalability.} The consensus latency of extant consensus protocols 
is often \emph{scale-limited}: it increases drastically when the number of 
concurrent requests or replicas 
increases~\cite{zookeeper,glendenning2011scalable}.

@@

\textbf{Hard to use.} Most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by \zookeeper.

Although there are some hardware-accelerated consensus 
protocols~\cite{consensusbox:nsdi16,netpaxos:sosr15,specpaxos:nsdi15,
nopaxos:osdi16} which are effective on reducing consensus latency, they are 
either unsuitable for general server programs or are not designed to be 
scalable on concurrent client connections. For instance, 
\dare~\cite{dare:hpdc15}, a novel consensus protocol, achieves the lowest 
consensus latency on a small number of client connections, but both its 
evaluation shows that its consensus latency increases quickly when  
more connections are added. Other recent 
works~\cite{nopaxos:osdi16,specpaxos:nsdi15,netpaxos:sosr15} 
leverage in-network serialization in a datacenter to safely skip 
consensus if packets arrive at replicas in the same order. 
These works require reconstructing a server program to use their new libraries 
for checking the order of packets, so they are not designed to run legacy 
server programs.

>>>>

\newcommand{\xxx}[0]{\textsc{APUS}\xspace}
\newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
\newcommand{\mytitle}[0]{\textbf {Problems on providing efficient fault 
tolerance to programs}}
\newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
and Deterministic Multithreading, Software Reliability}

@@

\begin{sloppypar}

State machine replication (\smr) is a powerful fault-tolerance 
concept~\cite{paxos:practical}. It runs replicas 
of same program on multiple nodes. To keep the replicas consistent, it invokes a 
distributed consensus protocol (typically 
\paxos~\cite{paxos:simple,lamport98parttime,paxos:complex}) to ensure that a 
quorum (typically majority) of the replicas agree on the input request sequence. 
\smr is proven to tolerate various failure scenarios, like network 
partition and packet loss.

The fault-tolerant benefit of \smr makes it particularly an attractive 
high-availability service for general server programs. Unfortunately, despite 
much effort, existing \smr systems are still hard to deploy, mainly due to 
three problems as elaborated below.

\subsection*{Issue 1: Poor scalability}
The consensus latency of extant consensus protocols 
is often \emph{scale-limited}: it increases drastically when the number of 
concurrent requests or replicas 
increases~\cite{zookeeper,glendenning2011scalable}.

@@

\subsection*{Issue 2: Hard to use}
Most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by \zookeeper. As an another 
example, in order to provide fault tolerance to a whole virtual machine, most 
of the existing \smr systems need to modify the hypervisor code which can be 
complex and error-prone.

\subsection*{Issue 3: High Consensus Latency}

The consensus latency of traditional \paxos 
protocols is notoriously high, incurring high performance overhead for server 
programs. A main reason is that messages of traditional TCP or UDP-based \paxos 
protocols have to go through OS kernel. For efficiency, \paxos protocols 
typically take the Multi-Paxos approach~\cite{paxos:simple}: it assigns one 
replica as the ``leader'' to invoke consensus requests, and the other replicas 
as ``backups'' to agree on requests. To agree on an input, at least one 
round-trip time (RTT) is required between the leader and a backup. Given that a 
ping RTT in LAN typically takes hundreds of \us, and that the request 
processing 
time of key-value store servers (\eg, \redis) is at most hundreds of \us, 
existing \paxos protocols incur high overhead in the response time of server 
programs.

Although there are some hardware-accelerated consensus 
protocols~\cite{consensusbox:nsdi16,netpaxos:sosr15,specpaxos:nsdi15,
nopaxos:osdi16} which are effective on reducing consensus latency, they are 
either unsuitable for general server programs or are not designed to be 
scalable on concurrent client connections. For instance, 
\dare~\cite{dare:hpdc15}, a novel consensus protocol, achieves the lowest 
consensus latency on a small number of client connections, but its 
evaluation shows that its consensus latency increases quickly when  
more connections are added. Other recent 
works~\cite{nopaxos:osdi16,specpaxos:nsdi15,netpaxos:sosr15} 
leverage in-network serialization in a datacenter to safely skip 
consensus if packets arrive at replicas in the same order. 
These works require reconstructing a server program to use their new libraries 
for checking the order of packets, so they are not designed to run legacy 
server programs.
